The binary liquid model for gravity-driven microchannel simulations

### 2010-10-25 Text/paper.tex
Minor style fixes in the abstract.

\title{The binary liquid model for gravity-driven microchannel simulations}
\date{\today}

\begin{document}

@@

\begin{abstract}
The motion towards exploration of nano- and microscale phenomena brings new
challenges to simulation tools. The continuous physics approach is limited on
those scales, therefore such methods as Molecular Dynamics (MD) or Lattice
Boltzmann Method (LBM) become appropriate. This work has aim to
reproduce the gravity driven microchannel flow of free surface liquid with the
help of the binary liquid lattice Boltzmann method. In the low capillary number
$Ca$ region the flow is thoroughly described by Bretherton \cite{bretherton},
where the deposition film thickness is proportional to $Ca^{2/3}$. The binary
liquid model is continuous interface multiphase model. Therefore, the issue of
how to properly resolve the interface to obtain proper correlations holds. In
the work we address the binary liquid parameters, as mobility $M$, surface
tension parameter $k$, the free energy constant $A$, grid resolution, to
properly simulate microchannel flow. The work is valuable for industry and
researchers willing to simulate Bretherton phenomena.
\end{abstract}

>>>>

\title{The binary liquid model for gravity-driven microchannel simulations}
\date{\today}
\newcommand{\Ca}{\mathrm{Ca}}
\newcommand{\todo}[1]{{\color{red}#1}}
\begin{document}

@@

\begin{abstract}
The motion towards exploration of nano- and microscale phenomena brings new
challenges to simulation tools. The continuous physics approach is limited on
those scales, and methods such as Molecular Dynamics (MD) or the Lattice
Boltzmann Method (LBM) become more appropriate. This work aims to
reproduce the gravity driven microchannel flow of a free surface liquid with the
help of the free-energy binary liquid lattice Boltzmann method. In the low capillary number
$\Ca$ regime, the flow is thoroughly described by Bretherton \cite{bretherton},
where the deposition film thickness is proportional to $\Ca^{2/3}$. The binary
liquid model we use is a continuous-interface multiphase model, which presents
the question of how to properly resolve the interface to obtain proper correlations \todo{between what?}.
In this work we investigate how the binary liquid model parameters and the grid resolution
need to be adjusted to properly simulate microchannel flows.  The presented results
should be of interest for industrial applications and to researchers simulating
Bretherton phenomena.
\end{abstract}
